A self-consistency check for unitary propagation of Hawking quanta

### 2016-12-10 Draft_BH_shells.tex
typo

\begin{equation}
	K_{ab} = \frac{1}{2} (\mathcal{L}_n g_{\alpha \beta}) e^\alpha_a e^\beta_b, \hspace{5mm} e^\alpha_a \equiv \frac{\partial x^\alpha}{\partial y^a},
\end{equation}
where $a,b \in \{t,\theta, \phi \}$ and $\mathcal{L}_n$ is the Lie derivative w.r.t to the normal vector $n_\alpha = g_{rr}^{-\frac{1}{2}} \partial_\alpha r = (0, g_{rr}^{-\frac{1}{2}}, 0 , 0)$. Lets look at the Lie derivative first

\begin{eqnarray}
	L_n g_{\alpha \beta} & = & n^\mu \partial_\mu g_{\alpha \beta} + \partial_\alpha n^\mu g_{\mu \beta} + \partial_\beta n^\mu g_{\alpha \mu}	\nonumber	\\
	& = & n^r \partial_r g_{\alpha \beta} + \partial_\alpha n^r g_{r \beta} + \partial_\beta n^r g_{\alpha r}	
\end{eqnarray}

>>>>

\begin{equation}
	K_{ab} = \frac{1}{2} (\mathcal{L}_n g_{\alpha \beta}) e^\alpha_a e^\beta_b, \hspace{5mm} e^\alpha_a \equiv \frac{\partial x^\alpha}{\partial y^a},
\end{equation}
where $a,b \in \{t,\theta, \phi \}$ and $\mathcal{L}_n$ is the Lie derivative w.r.t to the normal vector $n_\alpha = g_{rr}^{\frac{1}{2}} \partial_\alpha r = (0, g_{rr}^{\frac{1}{2}}, 0 , 0)$. Lets look at the Lie derivative first

\begin{eqnarray}
	\mathcal{L}_n g_{\alpha \beta} & = & n^\mu \partial_\mu g_{\alpha \beta} + \partial_\alpha n^\mu g_{\mu \beta} + \partial_\beta n^\mu g_{\alpha \mu}	\nonumber	\\
	& = & n^r \partial_r g_{\alpha \beta} + \partial_\alpha n^r g_{r \beta} + \partial_\beta n^r g_{\alpha r}	
\end{eqnarray}
